Social Visual Analytics: DevOps for Data Scientists

### 2015-03-23 interviews.tex
start interview prose and wrap lines

\gordon{Add user statistics here: so many users use the Research instance a lot, so many use it an intermediate amount, so many just tried it out. Simon to work up numbers on this. Also will get stats on number of notebooks, forks, stars, from Prateek's notebook.}

\subsection{Sharing of results}
Rick: ``I like being able to look at other people's notebooks.''

Clint: ``I can share it with people and copy it pretty readily. So if my supervisor wants to see what I've done or QA it, I can just send her a link.'' ``I think the best part about it is how easily you can share code... you can find a working example, rather than wearing out Google and finding questionable examples that may or may not work.''

@@

Taylor: ``I use it more for sharing code with other people, and for doing tutorials for iotools or hmr or explaining'' ``a lot of times I'll share the code, because I'm doing so much package development. I want people to see how the package works, so I clearly want them to see the code… I kind of write it just like I would write GitHub Markdown, where you have little code snippets and text, but RCloud lets me actually run the snippets” with results''

@@

@@

Jyothi: ``It's good that I can see the results but if I'm working and I need more room and I want to hide the results, I can't.” Could we have “an option to close the results window?”

@@

\subsection{Versioning not useful}
Rick: ``I don't need something that keeps track of every mistake I've made or every direction I've tried.” ``namespaces are already crowded, so trying to remember the names of notebooks is hard, much less the names of states within each notebook.''

\subsection{Web snafus}
Corey: ``“What frustrates me is that if I do leave this window for what feels like 5 or 7 minutes, it disconnects and I have to reconnect and run the whole notebook again.''

>>>>

\gordon{Add user statistics here: number of notebooks, forks, stars, users
who have done one of these things. Number of users who use RCloud a lot,
a moderate amount, or just tried it out.}

\subsection{Sharing of results}
Sharing of notebooks is the core feature of RCloud, and a popular one. Almost
everyone we spoke to praised this feature. By default, all notebooks are
publicly visible in RCloud, and notebooks can be found through the notebook tree
or search.

However, the method for sharing that users mentioned most is by sending links
through email. Clint says, ``I can share it with people and copy it pretty
readily. So if my supervisor wants to see what I've done or QA it, I can just
send her a link.''

``I think the best part about it is how easily you can share code... you can
find a working example, rather than wearing out Google and finding questionable
examples that may or may not work.''

@@

Taylor: ``I use it more for sharing code with other people, and for doing
tutorials for iotools or hmr or explaining'' ``a lot of times I'll share the
code, because I'm doing so much package development. I want people to see how
the package works, so I clearly want them to see the code… I kind of write it
just like I would write GitHub Markdown, where you have little code snippets and
text, but RCloud lets me actually run the snippets'' with results.

@@

Rick: ``I like being able to look at other people's notebooks.''

@@

Jyothi: ``It's good that I can see the results but if I'm working and I need
more room and I want to hide the results, I can't.'' Could we have ``an option
to close the results window?''

@@

\subsection{Versioning not useful}
Rick: ``I don't need something that keeps track of every mistake I've made or
every direction I've tried.'' ``namespaces are already crowded, so trying to
remember the names of notebooks is hard, much less the names of states within
each notebook.''

\subsection{Web snafus}
Corey: ``What frustrates me is that if I do leave this window for what feels
like 5 or 7 minutes, it disconnects and I have to reconnect and run the whole
notebook again.''
